---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r echo = FALSE, message = FALSE}
library(dplyr)
source("R/wiki_didyouknow.R")
source("R/wiki_inthenews.R")
source("R/wiki_onthisday.R")
source("R/wiki_randomfact.R")
```

# wikifacts

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/keithmcnulty/wikifacts/workflows/R-CMD-check/badge.svg)](https://github.com/keithmcnulty/wikifacts/actions)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/wikifacts?color=green)](https://cran.r-project.org/package=wikifacts)
<!-- badges: end -->

R package which generates strings containing random facts from current or historic Wikipedia main pages.  Intended for light-hearted support for scripts or apps that take a long time to execute.

## Installation

You can install the released version of wikifacts from [CRAN](https://CRAN.R-project.org) with:

``` {r eval = FALSE}
install.packages("wikifacts")
```

And the development version from [GitHub](https://github.com/) with:

``` {r eval = FALSE}
# install.packages("devtools")
devtools::install_github("keithmcnulty/wikifacts")
```

## Functionality

- `wiki_didyouknow()` generates string with random 'did you know' fact from Wikipedia main page
- `wiki_inthenews()` generates string with random 'in the news' fact from Wikipedia main page
- `wiki_onthisday()` generates string with random 'on this day' fact from Wikipedia main page
- `wiki_randomfact()` generates string with random fact from Wikipedia main page (one of the above selected randomly)

## Examples

``` {r}
wiki_didyouknow() %>% cat()
```

``` {r}
wiki_randomfact("2015-01-02") %>% cat()
```

Use with `cowsay`: 

``` {r}
cowsay::say(wiki_randomfact("2015-01-02"))
```

Generate a table of random facts by date (using `dplyr 1.0.0`):

``` {r}
date_tbl <- data.frame(date = seq(from = as.Date("2015-01-01"), to = as.Date("2015-01-14"), by = "days"))

date_tbl %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(fact = wiki_randomfact(date))
```
