---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r echo = FALSE, message = FALSE}
library(dplyr)
source("R/wiki_didyouknow.R")
source("R/wiki_inthenews.R")
source("R/wiki_onthisday.R")
source("R/wiki_randomfact.R")
```

# wikifacts

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/keithmcnulty/wikifacts/workflows/R-CMD-check/badge.svg)](https://github.com/keithmcnulty/wikifacts/actions)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/wikifacts?color=green)](https://cran.r-project.org/package=wikifacts)
[![CRAN status](https://www.r-pkg.org/badges/version/wikifacts)](https://CRAN.R-project.org/package=wikifacts)
[![Travis build status](https://travis-ci.com/keithmcnulty/wikifacts.svg?branch=master)](https://travis-ci.com/keithmcnulty/wikifacts)
[![Codecov test coverage](https://codecov.io/gh/keithmcnulty/wikifacts/branch/master/graph/badge.svg)](https://codecov.io/gh/keithmcnulty/wikifacts?branch=master)
<!-- badges: end -->

R package which generates strings containing random facts from current or historic Wikipedia main pages.  Intended for light-hearted support for scripts or apps that take a long time to execute.

## Installation

You can install the released version of wikifacts from [CRAN](https://CRAN.R-project.org) with:

``` {r eval = FALSE}
install.packages("wikifacts")
```

And the development version from [GitHub](https://github.com/) with:

``` {r eval = FALSE}
# install.packages("devtools")
devtools::install_github("keithmcnulty/wikifacts")
```

## Functionality

- `wiki_didyouknow()` generates random 'did you know' facts from Wikipedia main page
- `wiki_inthenews()` generates srandom 'in the news' facts from Wikipedia main page
- `wiki_onthisday()` generates random 'on this day' facts from Wikipedia main page
- `wiki_randomfact()` generates random facts from Wikipedia main page

## Examples

``` {r}
wiki_didyouknow() %>% cat()
```

``` {r}
wiki_randomfact() %>% cat()
```

Use with `cowsay`: 

``` {r}
cowsay::say(wiki_randomfact())
```

Generate multiple random facts:

``` {r}
wiki_randomfact(n_facts = 10, bare_fact = TRUE)

```
